---
title: "Streaming_KPI_Dashboard"
author: "HyunJoon Bok"
date: "August 25, 2020"
output: html_document
---

# Check Below links to finish send-out emails 
https://github.com/rstudio/blastula
https://solutions.rstudio.com/post/rstudio-connect-custom-emails-with-blastula/

```{r setup, include=FALSE}
setwd("C:/Users/bokhy/Desktop/alu_kpis")
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(gt)
library(blastula)
library(glue)

library(flexdashboard)
library(DT)
source("alu_kpis.R")
```

```{r data, include=FALSE}
ALU_kpis <- get_kpis()
# Get the KPIs for the most recent day in a list
one_day_kpis <-
  ALU_kpis %>%
  select(value) %>%
  head(1) %>% as.list()
```

```{r}
highlight_weekends <- function(data) {

  data %>%
    tab_style(
      style = cell_fill(color = "gray95"),
      locations = cells_body(
        columns = TRUE,
        rows = wday %in% c(1, 7)
      )
    )
}
```


## Summary of Business Health

The following table shows our business health KPIs. Each row represents a daily view of the KPIs that determine the success of our product. These are DAU (*Daily Active Users*), DAC (*Daily Active Customers*), the ratio DAC/DAU, our daily New Users and Churned Users, and, our Daily Revenue. If any KPIs are problematic, their values are shaded in light red.

```{r business_health_gt, echo=FALSE}
gt_health <-
  ALU_kpis %>%
  select(Service, date, value,wday) %>% 
  gt(rowname_col = "date", groupname_col = "Service") %>%
  tab_header(
    title = "Daily Unique Users",
    subtitle = "Last 7 days of KPIs shown for Product (weekend in gray)"
  ) %>% 
  highlight_weekends() %>%
  cols_hide(columns = vars(wday)) %>%
  cols_align(align = "right", everything()) %>%
  tab_options(table.width = px(740), data_row.padding = px(2.5)) %>%
  cols_width(everything() ~ px(740 / 7)) %>%
  opt_all_caps()
```


## Daily Users Chart

The following time-series plot gives us a picture of how our user-based KPIs have been performing over the last 30 days.

```{r ggplot_users, fig.align="center", echo=FALSE}
ALU_kpis %>%
  ggplot() +
  geom_line(aes(x = date, y = value,  color = Service)) +
  theme_tq() + 
  scale_color_tq() +
  labs(
    title = "Daily Unique Users per Service",
    x = "", y = "Users", color = "Service"
  ) +
  #theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.caption.position =  "plot",
    legend.position = "top"
  )
```


## Daily Playtime Chart

The following time-series plot gives us a picture of how our daily playtime revenue has been changing over time.

```{r ggplot_revenue, fig.align="center", echo=FALSE}
ALU_kpis %>%
  select(date, playtime, Service) %>%
  ggplot(aes(x = date, y = playtime, color = Service)) +
  geom_line(size = 1) +
  geom_point(size = 2, shape = 21, fill = "white", stroke = 1) +
  scale_y_continuous(position = "left",
                     label = label_number(suffix = " (Hrs)")) +
  labs(
    title = "Daily Playtime for each service",
    subtitle = "Playtime in Hours (Add-On and Built-in are Opt-in User Only)\n",
    x = "", y = ""
  ) +
  theme_minimal() +
  theme(
    plot.title.position = "plot",
    plot.caption.position =  "plot"
  )
```

```{r connect_email_setup, echo=FALSE}
render_connect_email(input = "business_health_email.Rmd") %>%
    attach_connect_email(
      subject = glue(
        "One or more KPIs ({total_exceed}) broke thresholds: \\
        {paste(names_exceed, collapse = ', ')}"
      ),
      attachments = "All_services.csv")

```